WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-02-22 article/Article.tex
rename COND_WRAP to WRAP_TYPES
darcs-hash:20060221211616-2fc9d-c3424e877108e660679eb550e61e41e9f04f1170.gz
rename WRAP to WRAP_TEMPLATE, as suggested by Zach
darcs-hash:20060222121542-2fc9d-ee33a59ee01e853026c3285d9624ff23785c8874.gz

  \item \verb$WRAP("mangled_suffix" "template parameters")$ -- When issued between \verb$WRAP_CLASS$
and \verb$END_WRAP_CLASS$, this command causes a particular template instantiation of
the current class to be wrapped. The parameter \verb$mangled_suffix$ is a suffix to
append to the class's name that uniquely identifies this particular template
instantiation, and "template parameters" are whatever should go between the \verb$< >$
template instantiation brackets. (Do not include the brackets.) If you are
wrapping a filter, there are simpler macros to use, which are defined at the
bottom of \verb$CreateCableSwigInputs$ and described below.

  \item \verb$COND_WRAP("mangled_suffix" "template parameters" "type list")$

>>>>

  \item \verb$WRAP_TEMPLATE("mangled_suffix" "template parameters")$ -- When issued between \verb$WRAP_CLASS$
and \verb$END_WRAP_CLASS$, this command causes a particular template instantiation of
the current class to be wrapped. The parameter \verb$mangled_suffix$ is a suffix to
append to the class's name that uniquely identifies this particular template
instantiation, and "template parameters" are whatever should go between the \verb$< >$
template instantiation brackets. (Do not include the brackets.) If you are
wrapping a filter, there are simpler macros to use, which are defined at the
bottom of \verb$CreateCableSwigInputs$ and described below.

  \item \verb$WRAP_TYPES("mangled_suffix" "template parameters" "type list")$
